Proposal Defense

### 2025-11-27 presentation/proposal/proposal.qmd
Edit

## Method: Data generation

@@

+ This study assumed the yield data were collected at the subplot level (total 1440 subplots).

@@

## Identifying the true best model among the five candidate models

+ Each of the candidate models are trained using the whole experiment data and then variable rate EONR are estimated for the whole field.

+ The estimated variable rate N recommendations are evaluated against the true variable rate N to evaluate the performance of the models (using profit loss relative to the true site-specific EONR as the criteria):

@@

## Model Selection

@@

## Simulation Results: Accuracy of the model selection approaches

```{r}
#| echo: false
#| results: 'asis'
tbl <- readRDS("main_selection_accuracy_table.rds")
invisible(flextable::save_as_image(tbl, path = "table_accuracy.png"))
knitr::include_graphics("table_accuracy.png")

```

>>>>

## Method: (Step 1) Data generation

@@

@@

## (Step 2) Identifying the true best model among the five candidate models

+ Train Each of the candidate models using the whole experiment data and then estimate variable rate EONR for the whole field.

+ Evaluate the performance of the models (using profit loss relative to the true site-specific EONR as the criteria):

@@

## (Step 3) Model Selection

@@
